%-------------------------
% Applied Scientist Resume - Jesus Mancilla
% Tailored from hybrid master to emphasize ML/LLM systems and engineering impact
% Base template: Aras Gungore (MIT) — adapted for Jesus Mancilla
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

% -------------- PAGE SETUP ------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{12pt}

\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.05in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \small #3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \small #3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}} 

%-------------------------------------------

\begin{document}

%---------- HEADING ----------
\begin{center}
  {\Huge\scshape Jesus Mancilla} \\[4pt]
  \textbf{Applied Scientist | AI/ML Systems Architect} \\
  \small
  LLMs, RAG, Evaluation, Vector Search, Retrieval Pipelines, Autonomous Agents, AI Systems Architecture\\
  \faMobile\ \href{tel:16503914301}{+1 650 391 4301}
  $|$
  \href{mailto:jesus@jgmancilla.com}{jesus@jgmancilla.com}
  $|$
  \faLinkedinSquare\ \href{https://www.linkedin.com/in/jegama}{LinkedIn.com/in/jegama}
  $|$
  \faGithub\ \href{https://github.com/jegama}{GitHub.com/jegama}
  $|$
  \faGlobe\ \href{https://www.jgmancilla.com/}{jgmancilla.com}
\end{center}

%---------- SUMMARY ----------
\section{Professional Summary}
Applied Scientist building production-grade \textbf{LLM/ML systems} end-to-end: \textbf{vector databases}, \textbf{retrieval pipelines}, \textbf{RAG}, \textbf{evaluation/observability}, and \textbf{autonomous agents}. Blend of industry impact (Meta, Roku, Walmart, Argomai) and academic rigor (peer-reviewed publications). Track record translating business goals into scalable architectures with clear metrics: \textbf{cut multipage doc classification from \textasciitilde90 min to $<$5 min} and \textbf{reduced weekly reporting from 6 hrs to $<$1 hr}; accelerated survey analysis from \textasciitilde30 hrs to $<$8 hrs via hybrid ML.

%----------- CORE SKILLS (ATS-optimized) -----------
\section{Technical Stack \& Domains}
\small
\textbf{LLMs/ML:} Retrieval, RAG, Evaluation, Prompting, Embeddings, Transformers, Scikit-learn, PyTorch, TensorFlow \\
\textbf{NLP:} Text classification, semantic search, vector stores, clustering, ranking \\
\textbf{Data/Apps:} Python, SQL, FastAPI, LangChain/LangGraph, React/Next.js, JS/TS \\
\textbf{Systems:} Enterprise architecture, service boundaries, domain models, NFRs, workflow automation \\
\textbf{Cloud/Tooling:} CI/CD, observability, Docker, Git \\
\textbf{Other:} Data viz, statistical inference; English \& Spanish

%----------- WORK EXPERIENCE -----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Argomai}{Houston, TX (Remote)}
      {Senior Applied Scientist (Consultant)}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Led enterprise \textbf{GenAI/ML architecture} (domains, service boundaries, data governance, NFRs) for customer-facing products; aligned initiatives with exec roadmaps.}
        \resumeItem{Engineered \textbf{vector databases}, \textbf{retrieval pipelines}, and \textbf{autonomous agents}; shipped a reusable component library (embeddings, prompt templates, orchestration SDK).}
        \resumeItem{Cut multi-page document classification from \textbf{\textasciitilde90 min $\rightarrow$ $<$5 min}; reduced stakeholder reporting from \textbf{6 h/wk $\rightarrow$ $<$1 h} through automation.}
        \resumeItem{Applied abstraction \& modularization to scale solutions across clients; improved latency/throughput consistency while lowering ops touchpoints.}
      \resumeItemListEnd

    \resumeSubheading
      {Meta}{Houston, TX (Remote)}
      {Senior Quantitative UX Researcher}{Jan 2024 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{Built a \textbf{hybrid ML classifier} for open-ended responses (clustering, few-shot, human-in-the-loop, multi-agent reasoning) to triage/analyze surveys at scale.}
        \resumeItem{\textbf{Reduced analysis time from \textasciitilde30 hrs to $<$8 hrs}; productized Python analytics tooling (stats, pipelines) for org-wide reuse.}
        \resumeItem{Fused behavioral editor logs with in-app surveys to create robust, multi-source datasets for model evaluation and product decisioning.}
        \resumeItem{Led longitudinal measurement for a new ML product with \textbf{500M+ MAU}; defined KPIs and bi-weekly tracking to inform iteration.}
      \resumeItemListEnd

    \resumeSubheading
      {Roku}{San Jose, CA}
      {Senior User Experience Researcher}{Jan 2021 -- Nov 2023}
      \resumeItemListStart
        \resumeItem{Developed the \textbf{Modular Survey Analysis System}: end-to-end \textbf{ML report generator} (stats + NLP categorization, clustering) over large-scale survey data.}
        \resumeItem{Created an \textbf{AI-powered indexed database} of UX \& CI research; \textbf{cut report generation from \textasciitilde4 hrs to $<$5 min} with ML automation and LLM summaries.}
        \resumeItem{Analyzed behavioral logs across \textbf{70M+ devices} to drive product decisions with quant evidence.}
      \resumeItemListEnd

    \resumeSubheading
      {Walmart Global Tech}{Sunnyvale, CA}
      {Senior User Experience Researcher}{Aug 2019 -- Nov 2020}
      \resumeItemListStart
        \resumeItem{Established KPIs and analytics for Sam’s Club mobile; integrated interaction telemetry with business metrics to inform roadmap and experimentation.}
      \resumeItemListEnd

    \resumeSubheading
      {Scrapworks Inc.}{Palo Alto, CA}
      {Data Scientist}{Sep 2017 -- Aug 2019}
      \resumeItemListStart
        \resumeItem{\textbf{60\% reduction} in forecasting error using deep learning for commodities futures; shipped dashboards over 20 years of sales data (\textbf{+30\% sales growth}).}
        \resumeItem{Initiated NLP merchandise classification (supported a patent filing); productionized multi-source data ingestion/cleaning.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- ADDITIONAL EXPERIENCE -----------
\section{Additional Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
    {Suggestic}{Mexico City, Mexico}
    {User Experience Researcher}{Dec 2016 -- Sep 2017}
      \resumeItemListStart
        \resumeItem {Data-driven testing and analysis for new app features; rapid prototyping informed by analytics.}
      \resumeItemListEnd

  \resumeSubheading
    {Stanford University}{Stanford, CA}
    {User Experience Researcher}{May 2016 -- Nov 2016}
      \resumeItemListStart
        \resumeItem {Researched stress detection using ML over multimodal data (>150 hours of car/biometric/video); contributed to 90\% accuracy algorithms.}
        \resumeItem{Co-authored papers on automotive UI and pedestrian interactions.}
      \resumeItemListEnd

  \resumeSubheading
    {ITAM}{Mexico City, Mexico}
    {User Experience Researcher}{Aug 2014 -- May 2016}
      \resumeItemListStart
        \resumeItem {Custom data visualizations and ML analysis on psychophysiological signals; personalized UX solutions across wearable, mobile, \& web.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- SELECTED PROJECTS -----------
\section{Selected Projects (Applied ML/LLMs)}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Research Librarian (AI Index for UX/CI)} — Semantic retrieval over an indexed research corpus using embeddings, vector stores, and custom ranking; improved findability and reuse across the org.}
    \resumeItem{\textbf{Modular Survey Analysis System} — End-to-end ML pipeline that auto-generates survey reports (stats + NLP categorization + clustering); enabled at-scale analytics with minimal analyst time.}
    \resumeItem{\textbf{Customer Support Bot (Ref Architecture)} — LLM-augmented support with RAG, evaluation/observability, and safety rails; blueprint for production conversational flows.}
  \resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeading{
      Instituto Tecnológico Autónomo de México (ITAM)}{}%
      {M.S. in Computer Science (HCI/AI Focus)}{2014 -- 2016}
    \resumeEducationHeading{
      Universidad de Colima}{}
      {B.A. in Psychology}{2009 -- 2013}
  \resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------
\section{Selected Publications}
  \resumeSubHeadingListStart
    \small{\item{
        {Ramos-Rivera, R. E., Santana Mancilla, P. C., Garcia-Mancilla, J., \& Gaytán-Lugo, L. S. (2025). Language models in education: Generative AI to optimize teacher performance analysis. InnovAcademica, 1(2), 74–85.}
    
        {Ramos-Rivera, R. E., Garcia-Mancilla, J., Cárdenas-Villa, G. E., \& Santana-Mancilla, P. C. (2024). Towards Improving Teacher Performance Assessment through Human-Centered AI-Powered Survey Analysis: An Approach Using Large Language Models (LLM). Avances en Interacción Humano-Computadora, 9(1), 261-264.}
    
        {Baltodano, Sonia, Jesus Garcia-Mancilla, and Wendy Ju. "Eliciting Driver Stress Using Naturalistic Driving Scenarios on Real Roads." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 298-309. ACM, 2018.} 
        
        {Currano, Rebecca, So Yeon Park, Lawrence Domingo, Jesus Garcia-Mancilla, Pedro C. Santana-Mancilla, Victor M. Gonzalez, and Wendy Ju. "¡Vamos!: Observations of Pedestrian Interactions with Driverless Cars in Mexico." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 210-220. ACM, 2018.} 

        {J. Garcia-Mancilla, J. E. Ramirez-Marquez, C. Lipizzi, G. T. Vesonder, and V. M. Gonzalez, “Characterizing negative sentiments in at-risk populations via crowd computing: a computational social science approach,” International Journal of Data Science and Analytics, Jun. 2018.} \\
        
        {\small For full list, see: jgmancilla.com/research-papers }
  }}
  \resumeSubHeadingListEnd

\end{document}
