%-------------------------
% Quantitative UX Researcher Resume - Jesus Mancilla
% Tailored from hybrid master to emphasize Quant UXR leadership, survey analytics, and experimentation
% Base template: Aras Gungore (MIT) — adapted for Jesus Mancilla
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

% -------------- PAGE SETUP ------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{12pt}

\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.05in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \small #3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \small #3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}} 

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------
\begin{center}
  {\Huge\scshape Jesus Mancilla} \\[4pt]
  \textbf{Staff User Researcher \,|\, Quant \& Mixed-Methods (ML-enabled)} \\
  \small
  Decision-driving insights at scale: survey \& log analytics, ML-assisted research ops, standardized evaluation \\
  \faMobile\ \href{tel:16503914301}{+1 650 391 4301}  $|$
  \href{mailto:jesus@jgmancilla.com}{jesus@jgmancilla.com}  $|$
  \faLinkedinSquare\ \href{https://www.linkedin.com/in/jegama}{LinkedIn.com/in/jegama}  $|$
  \faGithub\ \href{https://github.com/jegama}{GitHub.com/jegama}  $|$
  \faGlobe\ \href{https://www.jgmancilla.com/}{jgmancilla.com}
\end{center}

%---------- SUMMARY ----------
\section{Professional Summary}

Staff-level UXR leader blending \textbf{quantitative research at scale} with \textbf{ML/LLM tooling} to accelerate product decisions. Shipped reusable analysis pipelines, standardized metrics, and research ops that shortened feedback loops across \textbf{500M+ MAU} and \textbf{70M+ devices}. Noted for turning ambiguity into \textbf{operational, defensible insight systems} (e.g., open-ended survey analysis from \textbf{~30h to under 8h}; auto-reporting from \textbf{~4h to under 5m}; doc classification from \textbf{~90m to under 5m}). Bilingual (English/Spanish); strong cross-functional influence and executive-facing synthesis.

%----------- CORE SKILLS (ATS-optimized) -----------
\section{Technical Stack \& Domains}
\small
\textbf{Quant UX Research:} Survey design \& analytics, longitudinal tracking, KPI frameworks, experimentation, large-scale log analysis, dashboards \\
\textbf{Mixed-Methods:} Study design (interviews, diaries, ethnography, usability lab/remote/field), triangulation, research ops \\
\textbf{ML/LLMs:} Text classification, embeddings/vector search, clustering, RAG, prompting, evaluation/observability, HIL pipelines \\
\textbf{Tooling:} Python, SQL, statistical testing (t-tests/ANOVA/regression), FastAPI, LangChain/LangGraph, CI/CD, Docker \\
\textbf{Domains \& Scale:} Social/consumer media (500M+ MAU), TV/streaming (\textasciitilde70M devices), commerce, education, automotive/HF

%----------- WORK EXPERIENCE -----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Argomai}{Houston, TX (Remote)}
      {Senior Applied Scientist / Staff-Level UXR Consultant}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Owned enterprise \textbf{GenAI/ML architecture and platform governance} (domain models, service boundaries, data governance, NFRs) for insight workflows across clients.}
        \resumeItem{Led design and implementation of \textbf{vector DBs, retrieval pipelines}, and a reusable \textbf{AI component library} (embeddings, prompt templates, LangGraph-based agents).}
        \resumeItem{\textbf{Reduced document classification} from approximately \textbf{90m to under 5m} and PM reporting from \textbf{6h/wk to under 1h} via automation and retrieval.}
        \resumeItem{Deployed \textbf{LLM-powered survey analysis} workflows cutting manual review time and error risk; standardized governance across clients; frameworks later peer-reviewed.}
        \resumeItem{Ran generative and evaluative interviews (screeners, protocols, synthesis) and translated findings into metrics, roll-out plans, and decision checklists with executives to de-risk launches.}
      \resumeItemListEnd

    \resumeSubheading
      {Meta}{Remote}
      {Senior Quantitative UX Researcher}{Jan 2024 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{Deployed \textbf{hybrid ML + HIL classifier} for open-ended surveys; \textbf{cycle time from ~30h to under 8h} and \textbf{2$\times$ throughput} in a \textbf{500M+ MAU} context.}
        \resumeItem{Merged \textbf{editor logs, survey outputs, and classifier signals} (SQL warehouse joins) to drive data-backed roadmap decisions for a 500M+ MAU product.}
        \resumeItem{Shipped a reusable \textbf{Python analytics toolkit} (regressions/ANOVA/T-tests, pipelines) adopted across research teams; standardized metrics and reporting cadence.}
        \resumeItem{Ran longitudinal bi-weekly surveys and defined critical performance metrics to track classifier and product impact over time.}
        \resumeItem{Co-managed a global research panel and vendor partnerships; conducted interviews in Spanish to broaden signal quality across markets.}
      \resumeItemListEnd

    \resumeSubheading
      {Roku}{San Jose, CA}
      {Senior User Experience Researcher}{Jan 2021 -- Nov 2023}
      \resumeItemListStart
        \resumeItem{Built an \textbf{AI-powered indexed database} of UX/CI research, enabling org-wide self-serve discovery and faster executive reporting.}
        \resumeItem{Developed a \textbf{modular survey analysis system} with ML (stats + NLP clustering) and LLM summaries; \textbf{weekly survey reporting reduced from ~4h to under 5m}.}
        \resumeItem{Led quant/qual device research; integrated behavioral logs across \textbf{\textasciitilde70M devices} with lab and field findings to guide launches.}
        \resumeItem{Executed research on Customer Support site and call center tools; combined remote testing and IA validation to improve support UX.}
        \resumeItem{Mentored junior researchers and standardized research ops (Jira/Confluence backlogs, vendor management) across teams.}
      \resumeItemListEnd

    \resumeSubheading
      {Walmart Global Tech}{Sunnyvale, CA}
      {Senior User Experience Researcher}{Aug 2019 -- Nov 2020}
      \resumeItemListStart
        \resumeItem{Led analytics for Sam’s Club mobile in \textbf{Tableau}; established KPIs and dashboards linking \textbf{user-interaction + business metrics} to UX bets.}
        \resumeItem{Led cross-border (US/MX) standardization of surveys \& research workflows; designed and deployed surveys in \textbf{Medallia} and \textbf{SurveyMonkey}.}
        \resumeItem{Created \textbf{Kanban-based research ops boards} in Jira/Confluence to prioritize requests, visualize WIP, and coordinate stakeholders across markets.}
      \resumeItemListEnd

    \resumeSubheading
      {Scrapworks Inc.}{Palo Alto, CA}
      {Data Scientist}{Sep 2017 -- Aug 2019}
      \resumeItemListStart
        \resumeItem{\textbf{60\% reduction} in forecasting error; built dashboards over 20 years of sales data (\textbf{\textasciitilde30\% sales growth}).}
        \resumeItem{Initiated NLP merchandise classifier; productionized ingestion/cleaning pipelines across sources.}
      \resumeItemListEnd
      
  \resumeSubheading
    {Suggestic}{Mexico City, Mexico}
    {User Experience Researcher}{Dec 2016 -- Sep 2017}
      \resumeItemListStart
        \resumeItem{Data-driven UX iterations and advanced prototyping for health features; informed go/no-go decisions.}
        \resumeItem{Led transition from conversational to graphical interface using data insights and \textbf{Lean UX} loops (hypothesize $\rightarrow$ prototype $\rightarrow$ test); improved engagement and functionality.}
      \resumeItemListEnd

  \resumeSubheading
    {Stanford University}{Stanford, CA}
    {User Experience Researcher}{May 2016 -- Nov 2016}
      \resumeItemListStart
        \resumeItem{Designed on-road driver-stress protocol; \textbf{\textasciitilde90\%} elicitation, \textbf{\textasciitilde89\%} alignment with road events; published methods.}
        \resumeItem{Analyzed multi-modal data (vehicle, biometric, video); contributed to reproducible study assets.}
      \resumeItemListEnd

  \resumeSubheading
    {ITAM}{Mexico City, Mexico}
    {User Experience Researcher}{Aug 2014 -- May 2016}
      \resumeItemListStart
        \resumeItem{Psychophysiology + ML for stress/health; wearables \& usability research; Google Glass micro-interactions (IEEE).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- SELECTED PROJECTS -----------
\section{Selected Projects (Research Systems \& At-Scale Insight)}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Quant UX at Scale} — Hybrid classifier + validation; \textbf{time per study reduced from ~30h to under 8h}, \textbf{2$\times$ throughput} in \textbf{500M+ MAU} context.}
    \resumeItem{\textbf{Research Librarian (AI Index)} — Multi-engine semantic retrieval to surface prior insights and drive reuse.}
    \resumeItem{\textbf{Modular Survey Analysis System} — Auto-reports (stats + NLP clustering) for diverse surveys; large time savings.}
    \resumeItem{\textbf{Customer Support Bot (Blueprint)} — RAG + evaluation/observability + safety rails; solution-spotlight answers.}
  \resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeading{Instituto Tecnológico Autónomo de México (ITAM)}{}%
      {M.S. in Computer Science (HCI/AI Focus)}{2014 -- 2016}
    \resumeEducationHeading{Universidad de Colima}{}
      {B.A. in Psychology}{2009 -- 2013}
  \resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------
\section{Selected Publications}
  \resumeSubHeadingListStart
    \small{\item{
        {Ramos-Rivera, R. E., Santana Mancilla, P. C., Garcia-Mancilla, J., \& Gaytán-Lugo, L. S. (2025). Language models in education: Generative AI to optimize teacher performance analysis. InnovAcademica, 1(2), 74–85.}
    
        {Ramos-Rivera, R. E., Garcia-Mancilla, J., Cárdenas-Villa, G. E., \& Santana-Mancilla, P. C. (2024). Towards Improving Teacher Performance Assessment through Human-Centered AI-Powered Survey Analysis: An Approach Using Large Language Models (LLM). Avances en Interacción Humano-Computadora, 9(1), 261-264.}
    
        {Baltodano, Sonia, Jesus Garcia-Mancilla, and Wendy Ju. "Eliciting Driver Stress Using Naturalistic Driving Scenarios on Real Roads." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 298-309. ACM, 2018.} 

        {Currano, Rebecca, So Yeon Park, Lawrence Domingo, Jesus Garcia-Mancilla, Pedro C. Santana-Mancilla, Victor M. Gonzalez, and Wendy Ju. "¡Vamos!: Observations of Pedestrian Interactions with Driverless Cars in Mexico." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 210-220. ACM, 2018.} 

        {J. Garcia-Mancilla, J. E. Ramirez-Marquez, C. Lipizzi, G. T. Vesonder, and V. M. Gonzalez, “Characterizing negative sentiments in at-risk populations via crowd computing: a computational social science approach,” International Journal of Data Science and Analytics, Jun. 2018.}
        
        {\small For full list, see: jgmancilla.com/research-papers }
  }}
  \resumeSubHeadingListEnd

\end{document}
