%-------------------------
% Quantitative UX Researcher Resume - Jesus Mancilla
% Tailored from hybrid master to emphasize Quant UXR leadership, survey analytics, and experimentation
% Base template: Aras Gungore (MIT) — adapted for Jesus Mancilla
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

% -------------- PAGE SETUP ------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\footskip}{12pt}

\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.05in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \small #3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \\
      \small #3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}} 

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------
\begin{center}
  {\Huge\scshape Jesus Mancilla} \\[4pt]
  \textbf{Lead Mixed Methods UX Researcher} \\
  \small
  Quantitative \& Qualitative Methods • Research Leadership • Survey Analytics • Behavioral Data • Bilingual (EN/ES)\\
  \faMobile\ \href{tel:16503914301}{+1 650 391 4301} $|$
  \href{mailto:jesus@jgmancilla.com}{jesus@jgmancilla.com} $|$
  \faLinkedinSquare\ \href{https://www.linkedin.com/in/jegama}{LinkedIn.com/in/jegama} $|$
  \faGlobe\ \href{https://www.jgmancilla.com/}{jgmancilla.com}
\end{center}

%---------- SUMMARY ----------
\section{Professional Summary}
Bilingual \textbf{Lead UX Researcher} with 10+ years of experience spanning the U.S. and Latin America. Expert in combining \textbf{quantitative rigor and qualitative depth} to inform data-driven decisions. Built and led research programs across Meta, Roku, Walmart, and ITAM, mentoring junior researchers and developing scalable systems that compress analysis time, tie KPIs to user behaviors, and align cross-functional teams around evidence-based decisions.

%----------- CORE SKILLS (ATS-optimized) -----------
\section{Core Research Competencies}
\small
\textbf{Research Leadership:} Team mentoring, prioritization frameworks, executive reporting, research ops strategy \\
\textbf{Quant Methods:} Survey analytics, regressions, ANOVA, A/B testing, longitudinal and KPI development \\
\textbf{Qual Methods:} Interviews, diary studies, ethnography, usability testing, thematic synthesis \\
\textbf{Mixed Methods:} Behavioral log triangulation, survey-to-telemetry integration, insight frameworks \\
\textbf{Tools:} Python, R, SQL, Tableau, Jupyter, LangChain, FastAPI; Next.js for insight dashboards \\
\textbf{Languages:} Fluent in English and Spanish

%----------- WORK EXPERIENCE -----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Argomai}{Houston, TX (Remote)}
      {Senior UX Researcher}{Jan 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Partnered with execs to translate research findings into \textbf{metrics, roll-out plans, and decision checklists}; improved cycle time and confidence for go/no-go calls.}
        \resumeItem{Conducted \textbf{user interviews} for a new \textbf{GenAI platform} (screeners, protocols, synthesis) to validate value proposition and inform roadmap.}
        \resumeItem{Built reusable analysis components (\textbf{embeddings}, prompt templates, orchestration SDK) enabling faster \textbf{open-ended response} synthesis across studies.}
        \resumeItem{Authoring a paper and open-sourcing a multilingual QA evaluation pipeline: multi-step dataset generation (self-consistency $\rightarrow$ critique $\rightarrow$ refinement) + judge-centric evaluation with a deterministic audit layer.}
      \resumeItemListEnd

    \resumeSubheading
      {Meta}{Houston, TX (Remote)}
      {Senior Quantitative UX Researcher}{Jan 2024 -- Jan 2025}
      \resumeItemListStart
        \resumeItem{Built a \textbf{hybrid classifier} for open-ended survey responses (clustering, few-shot, human-in-the-loop, multi-agent reasoning) to triage at scale.}
        \resumeItem{\textbf{Reduced analysis time from \textasciitilde30 hrs to $<$8 hrs}; shipped Python analytics toolkit (regressions, ANOVA, T-tests) reused across teams.}
        \resumeItem{Ran large-scale mixed methods research with \textbf{500M+ MAU}; merged survey data and behavioral logs to guide product direction; \textbf{conducted interviews in Spanish} alongside other researchers running sessions in additional languages.}
      \resumeItemListEnd

    \resumeSubheading
      {Roku}{San Jose, CA}
      {Senior User Experience Researcher}{Jan 2021 -- Nov 2023}
      \resumeItemListStart
        \resumeItem{\textbf{Modular Survey Analysis System + AI-indexed repository:} ML-assisted survey reporting (stats + NLP categorization) and searchable knowledge base; \textbf{cut weekly report generation from \textasciitilde4 hrs to $<$5 min}.}
        \resumeItem{Mentored junior researchers in survey design and behavioral data analysis; managed \textbf{vendor relationships}, resource planning, and budget alignment.}
        \resumeItem{Led mixed-methods device research; combined lab studies with \textbf{behavioral log analysis across 70M+ devices} to inform product decisions and KPI targets.}
      \resumeItemListEnd

    \resumeSubheading
      {Walmart Global Tech}{Sunnyvale, CA}
      {Senior User Experience Researcher}{Aug 2019 -- Nov 2020}
      \resumeItemListStart
        \resumeItem{Established KPIs and analytics for Sam’s Club mobile app; integrated interaction data with business metrics to guide UX strategy.}
        \resumeItem{Led collaboration across bilingual teams in Mexico and U.S. to unify survey instruments and UX standards.}
        \resumeItem{Partnered with cross-functional design teams to ensure cultural and linguistic relevance in product testing.}
      \resumeItemListEnd

    \resumeSubheading
      {Scrapworks Inc.}{Palo Alto, CA}
      {Data Scientist}{Sep 2017 -- Aug 2019}
      \resumeItemListStart
        \resumeItem{Reduced forecasting error by \textbf{60\%} using deep learning; delivered dashboards over 20 years of sales data (\textbf{+30\% sales growth}).}
        \resumeItem{Initiated NLP classification and productionized data ingestion; informed product and operations decisions.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- ADDITIONAL EXPERIENCE -----------
\section{Additional Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
    {Suggestic}{Mexico City, Mexico}
    {User Experience Researcher}{Dec 2016 -- Sep 2017}
      \resumeItemListStart
        \resumeItem {Executed data-driven testing and analysis; designed advanced prototypes to validate feature concepts.}
      \resumeItemListEnd

  \resumeSubheading
    {Stanford University}{Stanford, CA}
    {User Experience Researcher}{May 2016 -- Nov 2016}
      \resumeItemListStart
        \resumeItem {Conducted research on driver stress using multimodal data; contributed to algorithms with \textbf{90\% accuracy}.}
        \resumeItem{Co-authored publications on automotive UI and pedestrian interactions.}
      \resumeItemListEnd

  \resumeSubheading
    {ITAM}{Mexico City, Mexico}
    {User Experience Researcher}{Aug 2014 -- May 2016}
      \resumeItemListStart
        \resumeItem {Analyzed psychophysiological signals; created custom visualizations to translate findings into design guidance.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- SELECTED PROJECTS -----------
\section{Selected Research/Systems Projects}
  \resumeSubHeadingListStart
    \resumeItem{\textbf{Research Librarian (AI Index)} — Improved \textbf{findability and reuse} of insights via embeddings, vector search, and custom ranking.}
    \resumeItem{\textbf{Modular Survey Analysis System} — ML-assisted pipeline to \textbf{auto-generate survey reports} with stats and NLP categorization.}
    \resumeItem{\textbf{Customer Support Insights} — RAG and evaluation framework to \textbf{summarize support knowledge} and instrument outcomes for leadership.}
  \resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationHeading{
      Instituto Tecnológico Autónomo de México (ITAM)}{}%
      {M.S. in Computer Science (HCI/AI Focus)}{2014 -- 2016}
    \resumeEducationHeading{
      Universidad de Colima}{}
      {B.A. in Psychology}{2009 -- 2013}
  \resumeSubHeadingListEnd

%----------- PUBLICATIONS -----------
\section{Selected Publications}
  \resumeSubHeadingListStart
    \small{\item{
        {Ramos-Rivera, R. E., Santana Mancilla, P. C., Garcia-Mancilla, J., \& Gaytán-Lugo, L. S. (2025). Language models in education: Generative AI to optimize teacher performance analysis. InnovAcademica, 1(2), 74–85.}
    
        {Ramos-Rivera, R. E., Garcia-Mancilla, J., Cárdenas-Villa, G. E., \& Santana-Mancilla, P. C. (2024). Towards Improving Teacher Performance Assessment through Human-Centered AI-Powered Survey Analysis: An Approach Using Large Language Models (LLM). Avances en Interacción Humano-Computadora, 9(1), 261-264.}
    
        {Baltodano, Sonia, Jesus Garcia-Mancilla, and Wendy Ju. "Eliciting Driver Stress Using Naturalistic Driving Scenarios on Real Roads." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 298-309. ACM, 2018.} 

        {Currano, Rebecca, So Yeon Park, Lawrence Domingo, Jesus Garcia-Mancilla, Pedro C. Santana-Mancilla, Victor M. Gonzalez, and Wendy Ju. "¡Vamos!: Observations of Pedestrian Interactions with Driverless Cars in Mexico." In Proceedings of the 10th International Conference on Automotive User Interfaces and Interactive Vehicular Applications, pp. 210-220. ACM, 2018.} 

        {J. Garcia-Mancilla, J. E. Ramirez-Marquez, C. Lipizzi, G. T. Vesonder, and V. M. Gonzalez, “Characterizing negative sentiments in at-risk populations via crowd computing: a computational social science approach,” International Journal of Data Science and Analytics, Jun. 2018.}
        
        {\small For full list, see: jgmancilla.com/research-papers }
  }}
  \resumeSubHeadingListEnd

\end{document}

